MCC Models

### 2019-03-12 papers/full_paper/models.Rmd
comments and edits up to model comparison

## Model utensils

```{r rsaUtils}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

var prior_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

@@

var lexicon1 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "triangle" :
utterance.label == "wug" ? obj.shape == "circle" : 
true
}

@@

  var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
   priorProbs, speakerOptimality) 
   observe(rsaPredictions, row.correct)

  }, data)

@@

@@

model_params_ex3$prior = list(
    c(1-prior_pref_same$prior,1-prior_pref_same$prior,prior_pref_same$prior), 
    c(prior_pref_same$prior,prior_pref_same$prior,1-prior_pref_same$prior), 
    c(1-prior_pref_diff$prior,1-prior_pref_diff$prior,prior_pref_diff$prior), 
    c(prior_pref_diff$prior,prior_pref_diff$prior,1-prior_pref_diff$prior),
    c(1-prior_novel_same$prior,1-prior_novel_same$prior,prior_novel_same$prior), 
    c(prior_novel_same$prior,prior_novel_same$prior,1-prior_novel_same$prior), 
    c(1-prior_novel_diff$prior,1-prior_novel_diff$prior,prior_novel_diff$prior), 
    c(prior_novel_diff$prior,prior_novel_diff$prior,1-prior_novel_diff$prior))

@@

    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])

@@

ex_3_cor_plot <- ex_3_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  mutate(data_mean = rep(ex_3_pred%>%filter(model == "data")%>%pull(mean),3),
         data_ci_lower = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_lower),3),
         data_ci_upper = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_upper),3))

>>>>

## Model utilities

```{r rsaUtils}
rsaUtils <- '
// three objects: triangle_1 on table 1, triangle_2 and circle_1 on table 2
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

// listener prior is over types, not tokens (we use uniformDraw on prior_objects)
var prior_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

@@

// two possible lexica, corresponding to meaning of words "dax" and "wug"
var lexicon1 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "triangle" :
utterance.label == "wug" ? obj.shape == "circle" : 
true
}

@@

    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
      priorProbs, speakerOptimality)

    observe(rsaPredictions, row.correct)
  }, data)

@@

**issue: here we are passing `adult_ex1_data` when we want `adult_ex1_data %>% filter(condition == "test")`**

@@

makePriorList = function(p){
  c(1 - p, 1 - p, p)
}

makeInversePriorList = function(p){
  c(p, p, 1 - p)
}

model_params_ex3$prior = list(
  makePriorList(prior_pref_same$prior), 
  makeInversePriorList(prior_pref_same$prior), 
  makePriorList(prior_pref_diff$prior), 
  makeInversePriorList(prior_pref_diff$prior), 
  makePriorList(prior_novel_same$prior), 
  makeInversePriorList(prior_novel_same$prior), 
  makePriorList(prior_novel_diff$prior), 
  makeInversePriorList(prior_novel_diff$prior)
)
```

@@

    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])

@@

ex_3_cor_plot <- ex_3_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  left_join(., ex_3_pred %>%
    ungroup()%>%
    filter(model == "data") %>%
    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
    select(-model)
  )
